resistanceModelNotesAndy

### 2015-03-16 resistanceModelNotesAndy.Rmd
progress notes

```{r}
max_gen <- 2 #just as exampel

@@

@@

1. check what the tilde does in R
1. copy the 'run' bit out of `malaria_code_andy.r` into a function 
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

>>>>

```{r}
max_gen <- 2 #just as example

@@

**13/3/15** 9.15-12.15 3hrs

A reproducible version of yesterdays bug.

```
x<-1
~
for(i in 1:10) x<-x+1
cat(x)
```
[R bug reporting](https://bugs.r-project.org/bugzilla3/enter_bug.cgi)

1. can I create a list of the 3 lists for results ?
Yes
Replace this  
results.list <- list()			
fitness.list <- list()
genotype.list <- list()	
with  
listOut <- list( results=list(), fitness=list(), genotype=list() )

Then find & replace  
results.list with listOut$results  
fitness.list with listOut$fitness
genotype.list with listOut$genotype

**16/3/15** monday 18.30

cut out lines 92 to 1740 into a runModel() function, later can subdivide it up

In max(combmat[, gencol]) : no non-missing arguments to max; returning -Inf
fixed by returning listOut from runModel()

@@

1. add a savePlots argument, to enable plotting without saving
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.
